Simulated Observations of Young Gravitationally Unstable Protoplanetary Discs

### 2013-03-14 young_pp_discs.tex
nearly done

In this paper we have presented radiative transfer simulations of a hybrid model comprising a 0.39$\, M_\odot$ self gravitating disc with radius 64$\,$au showing spiral density waves, surrounded by an envelope simulated as a contracting 10$\,M_\odot$ BE-sphere. The main results of these simulations are as follows:\smallskip
$\bullet$ CASA simulations of this model show that at a distance of 100$\,$pc, extraction of kinematics and structural information from the continuum and molecular lines is possible with ALMA band 7.\\
$\bullet$ Our simulations show that molecular features are predominantly seen in absorption against the hot mid-plane of self-gravitating protoplanetary discs, with emission only being seen where voids in the structure of the disc do not provide a bright continuum source to be absorbed.\\
$\bullet$ The quiescent nature of the envelope around such discs only obscures lines within $\pm\,$0.5 km$\,$s$^{-1}$ of the systematic velocity.\\
$\bullet$ The lines studied (OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2) taken together allow all regions of the disc to be sampled and the rotation of the disc to be constrained from the inner edge to the outer edge.\\
$\bullet$ Spiral structure in young embedded discs are dectectable at a wide range of inclination angles, they can be resolved spatially at angles close to face on and can be infered from position velocity diagrams at low inclination angles.\smallskip

@@

Big up results here!!

>>>>

In this paper we have presented radiative transfer simulations of a hybrid model comprising a 0.39$\, M_\odot$ self gravitating disc with radius 64$\,$au showing spiral density waves, surrounded by an envelope simulated as a contracting 10$\,M_\odot$ BE-sphere. The main results of these simulations are as follows:\newline
$\bullet$ CASA simulations of this model show that at a distance of 100$\,$pc, extraction of kinematics and structural information from the continuum and molecular lines is possible with ALMA band 7.\\
$\bullet$ Our simulations show that molecular features are predominantly seen in absorption against the hot mid-plane of self-gravitating protoplanetary discs, with emission only being seen where voids in the structure of the disc do not provide a bright continuum source to be absorbed.\\
$\bullet$ The quiescent nature of the envelope around such discs only obscures lines within $\pm\,$0.5 km$\,$s$^{-1}$ of the systematic velocity.\\
$\bullet$ The lines studied (OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2) taken together allow all regions of the disc to be sampled and the rotation of the disc to be constrained from the inner edge to the outer edge.\\
$\bullet$ Spiral structure in young embedded discs are dectectable at a wide range of inclination angles, they can be resolved spatially at angles close to face on and can be infered from position velocity diagrams at low inclination angles.\smallskip

@@

These results demonstrate that with next generation millimetre interferometers we will be able to probe the very earliest stages of circumstellar discs which feed thier growing protostar and eventually could become a planetary system. Our results show that these types of observations would be able to dectect whether or not these young disc are gravitationally unstable, which could have significant implications on the evolution of the disc, such as fragmentation and planetesimal formation \cite{Boley2009,Johnson2013,Gibbons2012}, chemical evolution I2011 and other stuff i'd mention if i could get on ads.
